The problem and promise of scale in animal social multilayer networks

### 2020-08-27 paper/manuscript.Rmd
tidy intro p3, p4

Social network analysis is a well-developed tool used to measure the
relationships of individuals and organization of social systems [@Krause_2009;
@Wey_2008; @Croft_2011]. It provides insight into the structure of social
communities, which can influence population dynamics and evolutionary processes
[@Pinter_Wollman_2013; @Kurvers_2014]. Despite the widespread use and innovation
of traditional social network analysis [@Webber_2019], it typically considers
sociality in a singular context, drastically simplifying the complexity of
animal social systems [@Finn_2019]. Extending traditional monolayer social
networks, multilayer networks explicitly consider social systems across
scale-dependent contexts [@Pilosof_2017]. Multilayer networks are composed of
multiple layers, each representing (i) different classes of individuals, e.g.
male or female, (ii) types of behaviours, e.g. grooming, travelling, or
foraging, (iii) spatial areas, e.g. local or regional, (iv) or temporal windows,
e.g. daily or seasonal [@Kivela_2014; @Porter_2018]. Multilayer networks are 
relatively novel to studies of animal behaviour [@Silk_2018; @Finn_2019] and 
integrating scale within these remains an unexplored opportunity to develop 
novel understanding of animal social systems.

We examined scale-dependent multilayer networks of behavioural, landscape, and
spatial ecology and applied this framework to caribou (*Rangifer tarandus*).
First, we test to what degree the social scale of relationships, spatial scale
of landscapes, and temporal scale of analysis influences our ability to
interpret complex social systems. Second, we address how variation in the
social, spatial, and temporal scale improves our understanding of the
relationship between social association and seasonal resource availability. We
conclude with potential future developments and applications of scale in
multilayer networks.

>>>>

Social network analysis is a well-developed tool used to measure the
relationships of individuals and organization of social systems [@Krause_2009;
@Wey_2008; @Croft_2011]. It provides insight into the structure of social
communities, which can influence population dynamics and evolutionary processes
[@Pinter_Wollman_2013; @Kurvers_2014]. Despite the widespread use and innovation
of traditional social network analysis [@Webber_2019], it typically considers
sociality in a singular context, drastically simplifying the complexity of
animal social systems [@Finn_2019]. Extending traditional monolayer social
networks, multilayer networks explicitly consider social systems across
scale-dependent contexts [@Pilosof_2017]. Multilayer networks are composed of
multiple layers, that can represent (i) different classes of individuals, e.g.
male or female, (ii) types of behaviours, e.g. grooming, travelling, or
foraging, (iii) spatial areas, e.g. local or regional, (iv) or temporal windows,
e.g. daily or seasonal [@Kivela_2014; @Porter_2018]. Multilayer networks are 
relatively novel to studies of animal behaviour [@Silk_2018; @Finn_2019] and 
integrating scale within multilayer networks remains an unexplored opportunity to develop 
novel understanding of animal social systems.

We examined scale-dependent multilayer networks of behavioural, landscape, and
spatial ecology and applied this framework to caribou (*Rangifer tarandus*).
First, we test to what degree the social scale of relationships, spatial scale
of landscapes, and temporal scale of analysis influences our ability to
interpret complex social systems. Second, we address how variation in social,
spatial, and temporal scales improves our understanding of the relationship
between social association and seasonal resource availability. We conclude with
potential future developments and applications of scale in multilayer networks.
